---
title: "Codebook"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Codebook

Codebook created on `r as.character(Sys.time())`

List of variables in summary_means.txt dataset

```{r }
names(tidySummary)
```

------------------------------

Variable name    | Description
-----------------|------------
subject          | participant ID - numeric between 1 and 30
activity         | activity name
domain           | indicates time or frequency domain
dimension        | 3-axial dimension component (x, y, z)
component        | acceleration component measured (body or gravity)
instrument       | instrument making measurement (accelerometer or gyroscope)
jerk             | indicates jerk measurement
magnitude        | indicates magnitude measurement
statistic        | indicates mean or standard deviation calculation
count            | number of observations used to calculate mean_value
mean_value       | mean value calculated for each observation

The dataset summary_means.txt is created by the run_analysis.R code and has the 
following structure:

```{r }
str(tidySummary, max.level = 2)
```

First few rows of the dataset:

```{r }
as_tibble(tidySummary)
```
